\documentclass{businessdoc}

% Metadata
\documenttitle{Business Core Document: Mission, Values, and Target Market}
\authorname{Jeremy Khoo \\ KK}
\dateofdocument{\today}

\begin{document}

\maketitle
\thispagestyle{empty} % Title page without header/footer

\section{Introduction}
This document outlines the core aspects of KKstudio, including its mission, values, and a detailed analysis of the target market. It serves as a foundation for strategic decision-making and aligning our efforts with long-term goals.

\section{Mission Statement}
Help Pomeranian owners do the best for their dogs, through anxiety treatments, and breed-specific care and education.

\section{Vision Statement}
The go-to resource for small dog owners by combining specialized care with educational initiatives that empower them to nurture happy, healthy pets.

\section{Core Value}
The guiding principles that drive our operations are:
\begin{itemize}
    \item \textbf{Holistic Care} Prioritizing emotional, physical well-being of small dogs through peronalized and thoughful services.
\end{itemize}

\section{Target Market Analysis}

\subsubsection{Demographics}
\begin{itemize}
    \item \textbf{Age:} Predominantly young professionals (25--40) and retirees (55+).
    \item \textbf{Gender:} Likely balanced, with many women and couples leading ownership.
    \item \textbf{Income:} Middle to high-income levels; Singaporeans are known to invest significantly in pet care.
\end{itemize}

\subsubsection{Psychographics}
\begin{itemize}
    \item Highly value pets as companions, especially in a city-focused lifestyle.
    \item Health-conscious and interested in premium, specialized care for their dogs.
    \item Open to educational content, particularly on managing anxiety and dietary needs.
\end{itemize}

\subsubsection{Behavioral Traits}
\begin{itemize}
    \item Willing to pay a premium for reliable, trusted services.
    \item Active on social media platforms and responsive to digital marketing campaigns.
    \item Likely to engage in workshops, events, or online courses about pet care.
\end{itemize}

\subsubsection{Pain Points}
\begin{itemize}
    \item High-density living can exacerbate small dog anxiety.
    \item Difficulty finding breed-specific guidance and trustworthy advice.
    \item Seeking convenience while balancing demanding work-life schedules.
\end{itemize}


\section{Conclusion}
Have sex

\end{document}

